\vspace{-2cm} Government websites as data: A methodological pipeline with application to the websites of municipalities in the United States

### 2018-07-25 paper/manuscript.tex
revisions to STM section

\subsubsection{Structural topic model}
% BRUCE HERE
A powerful and frequently used approach within the family of BoW methods is the use of topic models. This class of clustering methods relies on the co-occurrence of words within documents to form a set of semantically coherent topics. In order to compare the degree to which Republicans and Democrats prefer specific topics, we rely on the structural topic model, developed by \citep{Roberts2014}. Theoretically, the most widely-used form of topic model, latent dirichlet allocation, can also be used to test for the impact of a single covariate through a post-hoc comparison, but the structural topic model allows for multiple covariates, and also produced more meaningful topics in our experiments.

>>>>

\subsubsection{Analytical approach: Structural topic modeling}
% BRUCE HERE
In order to analyze content differences of government websites based on mayoral partisanship, we draw upon a recently-developed class of text-as-data methods, the structural topic model, developed by \citep{Roberts2014}. Topic. In order to compare the degree to which Republicans and Democrats prefer specific topics, we rely on the structural topic model, developed by \citep{Roberts2014}. Theoretically, the most widely-used form of topic model, latent dirichlet allocation, can also be used to test for the impact of a single covariate through a post-hoc comparison, but the structural topic model allows for multiple covariates, and also produced more meaningful topics in our experiments.
